Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2015-06-02 tese/arch01.tex

\begin{itemize}
 \item Text, Audio and Video communication using \ac{WebRTC}.
 \item Enrich communications by overlaying multiple media types.
 \item Ability to perform tasks on real-time collaborative environment.
 \item Ability to record and playback interactive multimedia.
 \item File sharing and collaborative edition.
\end{itemize}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.55\textwidth]{figures/archs.png}
	\caption{System Modules}
        \label{fig:modules}
\end{figure}
%RP as figuras têm de ser apresentadas. Figure~\ref{fig:modules} presents ...
Figure~\ref{fig:modules} presents the structure of our system which is divided into five modules.

@@

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.55\textwidth]{figures/arch.png}
	\caption{System Architecture}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{figures/apparch.png}
	\caption{App Architecture}
\end{figure}
%RP apresentar figura

\emph{Modernizr} and \emph{jQuery} will ensure that our application is compatible with the most popular web browsers.
\emph{Bootstrap} will be used to make the user interface more appellative and responsive. With \emph{Bootstrap} it is quite easy to develop applications that adapt to mobile devices with different screen sizes.
The \emph{Strophe} library will be essential to communicate with the \ac{XMPP} server.
%RP era este o sentido da frase? Ou entre cliente e servidor apenas?

\emph{TogetherJS} will be used for the collaborative component of our web application. Other libraries were considered but, as said before, \emph{TogetherJS} does not provide object storage giving us the ability to choose how to store collaborative objects.
%RP relê a frase. É mesmo isto que queres dizer? ``does not implement''

The synchronization between multimedia elements will be performed trough \emph{JavasSript} events.
%RP já não vais usar smil? Como fazes a sincronização. Explica, sff.

>>>>

\begin{itemize}
 \item Text, Audio and Video communication using \ac{WebRTC}.
 \item Enrich communications by overlaying multiple media types.
 \item Create annotations over video and voice content.
 \item Search and navigate through annotations.
 \item Structure presentation of the content.
 \item Ability to perform tasks on real-time collaborative environment.
 \item Ability to record and playback interactive multimedia.
 \item File sharing and collaborative edition.
\end{itemize}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\textwidth]{figures/archs.png}
	\caption{System Modules}
        \label{fig:modules}
\end{figure}
%RP as figuras têm de ser apresentadas. Figure~\ref{fig:modules} presents ...
Figure~\ref{fig:modules} presents the structure of our system which is divided into five modules.

@@

Each room will be associated to multiple Media-Types, interactive and non-interactive, discrete and continuous. This media types can be structured with chains of events. Some components of the user interface may not be synchronized to all participants, for example an help or suggestion window.

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\textwidth]{figures/arch.png}
	\caption{System Infrastructure}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{figures/apparch.png}
	\caption{App Architecture}
	        \label{fig:apparch}

\end{figure}
%RP apresentar figura
Figure~\ref{fig:apparch} presents the application architecture and the underlying technologies. \emph{Modernizr} and \emph{jQuery} will ensure that our application is compatible with the most popular web browsers.
\emph{Bootstrap} will be used to make the user interface more appellative and responsive. With \emph{Bootstrap} it is quite easy to develop applications that adapt to mobile devices with different screen sizes.
The \emph{Strophe} library will be essential to communicate with the \ac{XMPP} server.
%RP era este o sentido da frase? Ou entre cliente e servidor apenas?

\emph{TogetherJS} will be used for the collaborative component of our web application. Other libraries were considered but, as said before, \emph{TogetherJS} does not provide object storage giving us the ability to choose how to store collaborative objects. We assume that \emph{JavaScript} objects are enough for implementing our application but \emph{TogetherJS} provides the flexibility to change our storage model.
%RP relê a frase. É mesmo isto que queres dizer? ``does not implement''

The synchronization between multimedia elements will be performed trough chains of \emph{JavasSript} events, other animations can be implemented with \ac{SVG} embedded on \ac{HTML}.
%RP já não vais usar smil? Como fazes a sincronização. Explica, sff.

### 2015-06-02 tese/state04.tex

Real time collaboration applications have become a huge help on team tasks, providing a great boost on business, research and investigation velocity. Technologies like these are appearing along these days, but they were not be possible a few years ago because technology was limited or unavailable. Although today's technology is still limited on some aspects, we are doing progress in order to improve the web ecosystem, by creating standards and migrating to newer technologies.
%RP aqui dizes ``we are doing progress''. Parece que é parte do teu trabalho e que tens algo a ver com isso. Muda para frase impessoal

>>>>

Real time collaboration applications have become a huge help on team tasks, providing a great boost on business, research and investigation velocity. Technologies like these are appearing along these days, but they were not be possible a few years ago because technology was limited or unavailable. Although today's technology is still limited on some aspects, progress is being done in order to improve the web ecosystem, by creating standards and migrating to newer technologies.
%RP aqui dizes ``we are doing progress''. Parece que é parte do teu trabalho e que tens algo a ver com isso. Muda para frase impessoal
